Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2022-02-04 paper/paper.tex
WIP switch to other laptop

Each retinal ganglion cell (RGC) projects growth cones (referred to
as \emph{branches}) which carry a set of 4 receptors, $r_i$ indexed by $i$ and
expressed at levels determined by the cell soma's location on the
retinal grid. (Four ligands, $l_i$, are also expressed by RGCs, but these are not
used by the chemoaffinity simulation.) The expression of each receptor
varies only with respect to one spatial dimension.  Receptor expression gradients are
arranged in orthogonal pairs with the gradient of $r_0$ being orthogonal to
that of $r_1$. $r_2$, whose gradient is opposite to $r_0$, is orthogonal to
$r_3$.

>>>>

Each retinal ganglion cell (RGC) projects growth cones (referred to
as \emph{branches}) which carry a set of $m$ receptors, $r_i$ indexed by $i$ and
expressed at levels determined by the cell soma's location on the
retinal grid. ($m$ ligands, $l_i$, are also expressed by RGCs, but these are not
used by the chemoaffinity simulation.) The expression of each receptor
varies only with respect to one spatial dimension.

The minimum number of gradients required to provide a coordinate system on the
surface of the tectum within which axons could find a target location is
$m=2$, arranged in orthogonal directions. However if there are only two
gradients, imagining that one guides axons laterally and the other guides
axons in the caudal direction, then it is necessary for there to be an
additional `stopping mechanism' to prevent all of the axons eventually being
guided to the most lateral/caudal position. To avoid the need for a different
stopping mechanism, we chose to model \emph{opposing pairs of orthogonal
gradients} with $m=4$. With opposing gradients, an axon which interacts most
strongly with a gradient in the caudal direction would be drawn to the caudal
side of the tectum, whereas an axon whose strongest interaction was to climb a
gradient in the rostral direction would be drawn to the rostral side. There is
evidence that multiple gene expression gradients are found in the brain, with
examples of opposing pairs including XX and YY.

We defined 4 receptor expression gradients arranged in orthogonal pairs
with the gradient of $r_0$ being orthogonal to that of $r_1$. $r_2$, whose
gradient is opposite to $r_0$, was orthogonal to $r_3$.
